### 2018-06-27 Physics Notes/A2 Level/Turning Points/Overall Notes/Turning Points.tex
Tidied for upload to PMT

\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after. The horizontal velocity doesn't change, the vertical velocity is inverted. Therefore angle of incidence equals angle of reflection.\\

@@

\textbf{Refraction} - Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce. Newton was wrong.

@@

>>>>

\textbf{Reflection} - There is a short range repulsive force. These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after. The horizontal velocity doesn't change, the vertical velocity is inverted. Therefore angle of incidence equals angle of reflection.\\

@@

\textbf{Refraction} - There is a short range attractive force. Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce. Newton was wrong.

@@

The stopping potential causes no current to flow as it creates an electric field which attracts the electrons back to the plate.
